Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-08 programming23/artifact/main.tex
artifact checkpoint

TODO reason for sending

@@

\includegraphics[width=0.4\columnwidth]{out/lines-distribution.pdf}
\includegraphics[width=0.4\columnwidth]{out/editrange-distribution.pdf}

TODO mean stddev median P99

@@

\includegraphics[width=0.4\columnwidth]{out/timespan-distribution.pdf}
\includegraphics[width=0.4\columnwidth]{out/event-count-distribution.pdf}

TODO mean stddev median P99

@@

%% ---
\subsection*{Figure 4: Overview of Mode Usage}

>>>>

Lines 1-2 of \texttt{out/overview.txt} give the reason for sending:

\begin{verbatim}
 1504736 total logs = 1341348 nocheck + 156883 nonstrict + 6505 strict
  508572 due to module switch
\end{verbatim}

@@

From \texttt{out/summary-of-size-distributions.rktd}:

{\footnotesize
\verbatiminput{out/summary-of-size-distributions.rktd}
}

\begin{minipage}{0.5\columnwidth}
  \textbf{Lines:}\\
  \includegraphics[width=\columnwidth]{out/lines-distribution.pdf}
\end{minipage}\begin{minipage}{0.5\columnwidth}
  \textbf{Edit Range:}\\
  \includegraphics[width=\columnwidth]{out/editrange-distribution.pdf}
\end{minipage}

@@

See previous section for mean, stddev, median, and P99.

\begin{minipage}{0.5\columnwidth}
  \textbf{Timespan:}
  \includegraphics[width=0.4\columnwidth]{out/timespan-distribution.pdf}
\end{minipage}\begin{minipage}{0.5\columnwidth}
  \textbf{Event Count / Record Count:}
  \includegraphics[width=0.4\columnwidth]{out/event-count-distribution.pdf}
\end{minipage}

@@

Lines 3-8 of \texttt{out/overview.txt}:

\begin{verbatim}
 72235735 total forced strict type errors, 37027281 in module,
 curr 1111178 in edit regions,
 olde 938500 in edit regions
 595137 total type errors, 289698 in module,
 curr 14917 non-stx + 16007 syntax in edit regions,
 olde 13836 non-stx + 28565 syntax in edit regions
\end{verbatim}

%% ---
\subsection*{Figure 4: Overview of Type Analysis Modes}

Line 1 of \texttt{out/overview.txt} partitions logs by mode:

\begin{verbatim}
 1504736 total logs = 1341348 nocheck + 156883 nonstrict + 6505 strict
\end{verbatim}

Lines 9-13 of \texttt{out/overview.txt} partition sessions and report on upgrades and downgrades,
\emph{but} the final two numbers are incorrect (upgrade and downgrade) because they include
module switches:

\begin{verbatim}
 347598 sessions
  346956 single mode = 313509 nocheck + 32902 nonstrict + 545 strict
  512 multi mode projects
  341 mode upgrades
  320 mode downgrades
\end{verbatim}

Correct up/down-grade numbers are in \texttt{out/downgrade-count.txt}:

\includeverbatim{out/downgrade-count.txt}

TODO ^^^
